Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-10-25 analysis/paper/paper.Rmd
Update caption to match the figure

```{r year-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Equivalence test for the affect associated with the year of publication for (A) computational materials (code) and (B) data being made readily available to the public. A test for practical equivalence indicated that there was no effect of year of publication on computational materials (code) being shared. A test for practical equivalence was undecided in finding effect of year of publication on supporting data being shared. The region of practical equivalence (ROPE) is shown between two dotted lines. If the entire distribution falls within the ROPE, the hypothesis is accepted. If the entire distribution falls outside the ROPE, the hypothesis is rejected. In some cases the data do not provide a definitive answer and the decision on H0 is undecided. Here, year is treated as a continous variable to determine if there are changes over time in the likelyhood of sharing code and data.', cache=FALSE, fig.env='figure'}

>>>>

```{r year-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Equivalence test for the affect associated with the year of publication for (A) computational materials (code) and (B) data being made readily available to the public. A test for practical equivalence was unable to detect an effect of year of publication on computational materials (code) being shared. A test for practical equivalence found that there was no effect of year of publication on the availability of supporting data. The region of practical equivalence (ROPE) is shown between two dotted lines. If the entire distribution falls within the ROPE, the hypothesis is accepted. If the entire distribution falls outside the ROPE, the hypothesis is rejected. In some cases the data do not provide a definitive answer and the decision on H0 is undecided. Here, year is treated as a continous variable to determine if there are changes over time in the likelyhood of sharing code and data.', cache=FALSE, fig.env='figure'}
